% Hashtux SAD document
%
% Template by Jonas Kahler
% December 2015
% Preamble
\documentclass[11pt,a4paper]{report}

\usepackage{titlesec}
\titleformat{\chapter}[display]
        {\normalfont\huge\bfseries}
        {\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titlespacing*{\chapter}{0pt}{-80pt}{20pt}

% Begin of document
\begin{document}

% Title section
\title{Hashtux - SAD Document}
\author{Aman Dirar \and Jerker Ersare \and Jonas Kahler \and Dennis Karlberg
        \and Niklas le Comte \and Marco Trifance \and Ivo Vryashkov \\ \\
        BSc. Software Engineering and Management, \\
        Department of Applied IT, \\ Gothenburg University}
\date{December 2015}
\maketitle

% Table of content
\tableofcontents


% Beginning of text
% Introduction Chapter
\chapter{Introduction}

% Product Vision
\section{Vision}
\begin{quote}
\textit{``HashTux is a platform for easy access to multiple social media feeds
based on user’s search where the user has the option to filter information based
on his/her preferences.''}
\end{quote}
{\it HashTux} is a web-based service that displays the latest pictures, videos
and status updates for a given hashtag. Media files and status updates are
fetched from multiple social media sources and displayed in a web interface
optimized for full­screen view ­ ideal for a conference or party context, having
a screen illustrating the different viewpoints of the chosen keyword subject.
\newline
As time passes, the different content objects come and go, new ones fade in
replacing the old ones. Videos start playing automatically. The objects on the
screen are ordered automatically so that all space on the screen is used
properly.\newline
There is already successful software that does this for twitter only
(Tweetdeck). Our selling point is that in addition to this we want to include
content from multiple sources (also including instagram and youtube, but ideally
with a modular implementation that easily allows adding more) and also combine
it with multiple media formats, including video automatically playing.\newline
If there is a massive amount of content within a short time interval, our
application will display the content rated as most popular or from the most
trusted sources. To fetch older information we want to include a time scroll
functionality.\newline
We use CouchDB as our document-based database. Also, to ensure the system to
have a constant up-time even in the case of a failure or maintenance in one or
more servers. Our goal is to have the system running on several servers, so that
the system will have a constant uptime even though one or more of the servers
will be offline or in maintenance.\newline

% Target audience
\section{Target Audience}
\begin{description}
  \item[Event and conference hosts.] \hfill \\
  To easily show the latest multimedia from your event.
  \item[Social media users.] \hfill \\
  For the ease of use, fun experience, and the all-in-one solution.
  \item[General commercial use.] \hfill \\
  Illustrate recent updates for a product or company name.
\end{description}

% Domain
\section{Domain}
\begin{itemize}
  \item Information
  \item Social Media
  \item Trends
\end{itemize}
Giving internet users information on current trends, news and events on social
media.

% Business Cases
\section{Business Cases}

% Scope
\section{Scope}


% Archutectural Drivers
\chapter{Architectural Drivers}
\section{Functional Requirements}
\section{Quality Requirements}
\subsection{Scenario Analysis}
\section{Constraints}
\section{Tactics}
\subsection{Risks, Tradeoff and Sensitivity Points}

\chapter{Architectural Mechanisms}
\section{Analysis, Design and Implementation Mechanisms}

\chapter{System Characteristics and Challenges}
\section{Characteristics}
[Resource Sharing, Opennes, Cuncurrency, Scalability,
Fault Tolerance, Transparency]
\section{Challenges}
[Security, Privacy, Performance, Heterogeneity, Integrity,
Reliability, Availability]

\chapter{Use Case View}
\section{Significant Use Cases (Use Case Diagram and descriptions)}
\section{Use Cases realization (Sequence State Diagrams)}

\chapter{Logical View}
\section{Presentation Layer}
\section{Services Layer}
\section{Data Layer}

\chapter{Deployment View}

\chapter{Data View}

\end{document}