% LaTeX layout by Jonas Kahler, jonas@derkahler.de
% HashTux SAD Document
% Group Tux:
% Aman Dirar, Jerker Ersare, Jonas Kahler, Dennis Karlberg
% Niklas le Comte, Marco Trifance, Ivo Vryashkov
% Appendix
\label{appendix}
\appendix

% Reference to APIs Terms of Use
\hypertarget{appb}{
\chapter[Reference to APIs Terms of Use]{Reference to APIs\\ Terms of Use}}
In our implementation we ensured hashtux.com to be compliant with the APIs Terms
of Use and Limitations. Any modification or increment to the current
implementation should be carried out within the limits defined by the legal
documents listed below.

%%% Twitter
\subsubsection{Twitter}
{[Twitter, Inc, 2015]} Terms of Use. \newline
Available at: \href{https://dev.twitter.com/overview/terms}
   {dev.twitter.com/overview/terms} \newline
{[Accessed: 16 December 2015]} \\ \\
{[Twitter, Inc, 2015]} Developer Policy. \newline
Available at: \href{https://dev.twitter.com/overview/terms/policy}
   {dev.twitter.com/overview/terms/policy} \newline
{[Accessed: 16 December 2015]} \\ \\
{[Twitter, Inc, 2015]} Developer Agreement. \newline
Available at: \href{https://dev.twitter.com/overview/terms/agreement}
   {dev.twitter.com/overview/terms/agreement} \newline
{[Accessed: 16 December 2015]} \\ \\
{[Twitter, Inc, 2015]} Display Requirements. \newline
Available at: \href{https://about.twitter.com/company/display-requirements}
   {about.twitter.com/company/display-requirements} \newline
{[Accessed: 16 December 2015]}

%%% YouTube
\subsubsection{YouTube}
{[YouTube, Inc, 2010]} Terms of Service. \newline
Available at: \href{https://www.youtube.com/t/terms}
   {www.youtube.com/t/terms} \newline
{[Accessed: 12 December 2015]} \\ \\
{[YouTube, Inc, 2010]} Monetization Guidelines. \newline
Available at: \href{
https://developers.google.com/youtube/creating_monetizable_applications}
   {developers.google.com/youtube/creating\textunderscore
   monetizable\textunderscore applications} \newline
{[Accessed: 12 December 2015]} \\ \\
{[YouTube, Inc]} Google Software Principles \newline
Available at: \href{http://www.google.com/about/company/philosophy/}
   {http://www.google.com/about/company/philosophy/} \newline
{[Accessed: 12 December 2015]} \\ \\
{[YouTube, Inc]} Branding Guidelines \newline
Available at: \href{https://developers.google.com/youtube/branding_guidelines}
  {developers.google.com/youtube/branding\textunderscore guidelines} \newline
{[Accessed: 12 December 2015]}

%%% Instagram
\subsubsection{Instagram}
{[Instagram, 2015]} Platform Policy. \newline
Available at: \href{https://www.instagram.com/about/legal/terms/api/}
   {www.instagram.com/about/legal/terms/api/} \newline
{[Accessed: 15 December 2015]} \\ \\
{[Instagram, 2015]} Terms of Use. \newline
Available at: \href{https://www.instagram.com/about/legal/terms/}
   {www.instagram.com/about/legal/terms/} \newline
{[Accessed: 15 December 2015]} \\ \\
{[Instagram, 2015]} Privacy Policy. \newline
Available at: \href{https://www.instagram.com/about/legal/privacy/}
   {www.instagram.com/about/legal/privacy/} \newline
{[Accessed: 15 December 2015]}